Thomas et al. 2025

### 2025-01-11 IndividualStudies/AT_2025.qmd
EOD commit third try

---
title: "Thomas et al. 2025"
subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
format: 
  html:
    embed-resources: false
standalone: false
---

<!-- Data overview
Two lipid probes, PA and PE for a single cell line
 -->

>>>>

---
title: "Thomas et al. 2025"
subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
format: 
  html:
    embed-resources: false
standalone: false
---
s
<!-- Data overview
Two lipid probes, PA and PE for a single cell line
 -->
